\section{Introduction}


\subsection{Obective}

The objective is to provide a clear picture on the DM management products, including description, characterization and dependencies.


\subsection{Definitions}

Following definitions are relevant for this document.


\subsubsection{Product} \label{sec:product}

A product is a component of the DM product tree, that contribute to satisfy the DM requirements.

Each product is characterize by:

\begin{itemize}
  \item \textbf{Name}: it is the main identification of the product. In some cases a \textit{short name} can be provided for documentation purposes.
  \item \textbf{Unique Key}: it is a unique string mainly for programmatic usage. The product manager/owner can provide one, or it will be assigned by the Architecture team.
  \item \textbf{Owner}: who is responsible for the quality and acceptance of a particular product (\citeds{LDM-294} \S6.6).
  \item \textbf{Manager}: {T/CAM} who has managerial and financial responsibility for the engineering teams within DM (\citeds{LDM-294} \S6.14.1).
  \item \textbf{WBS}: the WBS identification.
  \item \textbf{Team}: the team in which the product is developed.
  \item \textbf{Description}: it provides a short overview of the product purpose.
  \item \textbf{Git Package}: the Git package that implementes the product.
  \begin{itemize}
    \item \textbf{software products}: it shall be the top levelpackage as per \citeds{DMTN-106} definition. 
    \item \textbf{services}: it should be the Git package where the Dockerfile defining the service is defined. The same repository could be used to keep under configuratino control other configuration files related to kubernettes definition (except secrets).
  \end{itemize}
  \item \textbf{Dependencies}: the list of products required to implement this product.
  \item \textbf{Upstream Products}: the list is products that use this product.
  \item \textbf{Links}: internet links that provide inportant information in order to clearly define the product.
  \item \textbf{Documentation}: list of Rubin documents that characterize the product.
  \item \textbf{Requirements}: list of requirements that are related in the model to the product.
\end{itemize}


\subsubsection{Software Product} \label{sec:swproduct}

Please refer to \citeds{DMTN-106} section \$2 for the Software Product definition.


\subsubsection{Product Tree} \label{sec:ptree}

The product tree is the graphical representation of the DM products.


\subsubsection{Dependencies} \label{sec:dependencies}

The dependencies listed in this document are functional dependencies.
The aim is to provide, for each product, the list of other products needed for its implementation or execution. 


\subsection{Applicable Documents}

Following documents are applicable:

\citeds{LDM-294} Data Management Organization and Management\\
% \citeds{LDM-148} Data Management System Design\\


\subsection{Document Overview}

Information in sections \ref{sec:top} and \ref{sec:sups} is extracted from MagicDraw and provides:

\begin{itemize}
\item the DM top level product tree: it includes all products required to satisfy the DMS requirements (\citeds{LSE-61}).
\item the DM support product tree: it includes all products required for construction and maintenance.
\end{itemize}

The information regarding the Git packages implementing the above products (in sections \ref{sec:top} and \ref{sec:sups}) is provided in section \ref{sec:low}. 
This information is extracted from GitHub.

The section \ref{sec:nondm} lists all non DM products that are required in order to fulfill the DMS requirements.
This information is extracted from MagicDraw.
No GitHub package details are provided for these products. 

The last section \ref{sec:jiracomponents} will document all components in the DM Jira project.
 

\subsection{Consistency and Completeness}\label{sec:cons-comp}

The information collected in the product tree shall be consistent and complete.

In order to be consistent, following rules need to be fulfilled:

\begin{itemize}
\item Facilities: shall host Enclaves
\item Enclaves: shall host services
\item Services: shall be implemented using DM Software Products or COTS
\item DM Software Products: shall have only one GitHub package
\item Low level dependencies to be made explicit in section 4
\item Dependencies to 3rd party libraries should (not yet, but will be) derived from GitHub
\item COTS and 3rd party libraries: shall have a link to a documentation page available in the global internet
\end{itemize}

In order to be complete, following rules need to be fulfilled:

\begin{itemize}
\item All products shall have an owner
\item All packages (subsection, paragraphs) shall have a manager
In case of multiple managers in the underlying products, no manager is specified and Arch Team will review it.
\item Each manager and each owner needs ensure that:
\begin{itemize}
\item She/he is the right person of taking care of that package/product
\item The information provided for each package/product is sufficient to characterize it.
\end{itemize}
\item Architecture Team shall ensure the consistency of the document following the rules listed above.
\end{itemize}


\newpage
\section{Top Level Product Tree}\label{sec:top}

The products listed in this section are maintained in MagicDraw by the DM System Engineering group. 

These products are meant to be operational, i.e. will process the survey source data and produce L1 or L2 data products, or will be distributed to permit the external collaborators and the science community to provide their contribution to the project.

These products are organized and maintained in MagicDraw by the DM System Engineering group.

\newpage
\subsection{Data Management Operational Products}\label{sec:dmtop}

\input{Main}


\newpage
\section{Supporting products}\label{sec:sups}

This section will list all DM products that are not involved in the operational data processing activities. 
However these products have an important role for construction and maintenance.

These products are organized and maintained in MagicDraw by the DM System Engineering group.
\newpage
\subsection{DM Development and Maintenance products}
\input{Development}


\newpage
\section{GitHub Packages}\label{sec:low}

This section lists the GitHub packages related to the DM products listed in previous sections \ref{sec:top} and \ref{sec:sups}.
The detailed information is extracted from GitHub.

The information provided includes, when available, the list of dependencies tracted from the ups table file.
Note that the release procedure as described in \citeds{DMTN-106} 
can be applied to a software product only if all dependencies 
are not used in other software products. If this is not the case, only one of these software products can be released.

As it can be evinced by a quick inspection in the following subsections, 
all Science Pipelines software products share a large number of dependencies. 
Therefore, the only releasebale software product, at the time of writing (July 2020) 
is the Science Pipeline distribution.

\input{git_pkgs_section.tex}


\newpage
\section{Non DM Products}\label{sec:nondm}

This section will list non DM products that are relevant in order to fulfill DMS requirements.


\newpage
\section{DM Jira Components}\label{sec:jiracomponents}

This section will list the components used in the DM Jira project.
Some of them are crealy related to a product included in the product tree or a low level git package.
Other Jira components are not mapped in the above sections, and will be described here.

The information should be extracted from Jira automatically and checks are executed in order to mach it with the information existing in MagicDraw and GitHub.
